The \project{UNRAVE} catalog

### 2016-08-12 article/unrave.tex
Added a bad abstract

\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\thecannon}{\project{The~Cannon}}
\newcommand{\acronym}[1]{{\small{#1}}}
\newcommand{\rave}{\project{\acronym{RAVE}}}
\newcommand{\logg}{\log g}
\newcommand{\Teff}{T_{\mathrm{eff}}}
\newcommand{\argmin}[1]{\underset{#1}{\operatorname{argmin}}\,}

@@

\title{The \project{UNRAVE} catalog of stellar astrophysical parameters and chemical abundances}

@@

\author{Some combination of: Hawkins, Ness, Hogg, HWR, Gilmore, Matijevic, RAVE collaboration}
%\altaffiltext{3}{\texttt{arc@ast.cam.ac.uk}}

\begin{abstract}
% Gaia will release stuff
% Much we want to do will involve chemistry + kinematics
% RAVE has the largest overlap with Gaia DR1, but chemistry is unavailable for most stars
% We perform an independent analysis of RAVE spectra w/ The Cannon, censoring, + upgrades, to derive astrophysical parameters and detailed chemical abundances.
% We produce a catalog of up to N abundances for X stars, constituting the largest
% catalog of chemical abundances that overlap with Gaia by a factor of X.

\end{abstract}

>>>>

\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\thecannon}{\project{The~Cannon}}
\newcommand{\acronym}[1]{{\small{#1}}}
\newcommand{\rave}{\project{\acronym{RAVE}}}
\newcommand{\logg}{\log g}
\newcommand{\teff}{T_{\mathrm{eff}}}
\newcommand{\argmin}[1]{\underset{#1}{\operatorname{argmin}}\,}

@@

\title{The \project{UNRAVE} catalog}

@@

\author{Some combination of: Gerry Gilmore, Keith Hawkins, David W. Hogg, Gal Matijevic, Melissa Ness, Hans Walter-Rix, and the \project{RAVE} collaboration}
%\altaffiltext{3}{\texttt{arc@ast.cam.ac.uk}}

\begin{abstract}
On 14 September 2016 the \project{Gaia} mission will release positions, proper motions, and parallaxes for about two million stars.  Most studies intending to make use of those data would benefit enormously from stellar chemical abundances.
  The RAdial Velocity Experiment (\project{RAVE}) survey has acquired spectra for approximately 280,000 stars in common with the first \project{Gaia} data release, constituting the largest overlap of any stellar spectroscopic sample.  Here we perform an independent analysis of the \project{RAVE} spectra using a new non-parametric version of \thecannon.  We deliver stellar astrophysical parameters ($\teff$, $\logg$) and chemical abundances of up to 8 elements (Fe, Na, Mg, Al, C, N, Ti, Ca) for X stars.  The typical precision in abundances is $X.XX$~dex.  We validate our results internally from repeat visits, and externally against existing high-resolution spectroscopic surveys. 
\end{abstract}
